Flatiron cleaning

### 2022-04-06 Rmd/Serous Actual weight rdi analysis.Rmd
Add Rmd for limited analysis on serous histology OC + fix carbo only analysis

# `r emo::ji("spiral_notepad")` This report is using **actual weight**

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology))

@@

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

### For Upfront Surgery
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
`imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
`imp_stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
`imp_stagecat + histology + imp_debulking` 
```{r rdi continous}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
`imp_stagecat + histology` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ `
`RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +`
`raceeth + ageatdx + stagecat + histology + debulking` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%

>>>>

# `r emo::ji("spiral_notepad")` This report is using **actual weight** in OC with **SEROUS** histology.

@@

- include patients whose histology of SEROUS CANCER    
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) %>% 
  filter(histology == "Serous")

@@

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking,
        data = data)
nonimp_cox_model

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking
       ))

@@

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

### For Upfront Surgery
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking,
        data = data)
nonimp_cox_model

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking
       ))

@@

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(histology == "Serous") %>% 
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
`imp_stagecat + imp_debulking` 
```{r Table 5 HR adjusted rdi group}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
`imp_stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
`imp_stagecat + imp_debulking` 
```{r rdi continous}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
`imp_stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ `
`RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +`
`raceeth + ageatdx + stagecat + debulking` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%

  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + debulking, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
